Importance of depth refugia for reef resilience and intervention on the Great Barrier Reef under future climate change

### 2025-10-13 paper/paper.qmd
Remove statement from acknowledgement
No ecoRRAP data was used

This research was funded by the Reef Restoration and Adaptation Program and facilitated by
the Australian Institute of Marine Science. The authors acknowledge thermal projection data
sourced from HighResCoralStress datasets, model parameterisation data sourced from the
Ecological Intelligence for Reef Restoration (EcoRRAP) subprogram, larval transition
probability data derived from the eReefs GBR1 hydrodynamic model, and spatial and depth data
available from the Great Barrier Reef Marine Park Authority. The eReefs Project is a
public-private collaboration between Australia’s leading operational and scientific research
agencies, government, and corporate Australia.

>>>>

This research was funded by the Reef Restoration and Adaptation Program and facilitated by
the Australian Institute of Marine Science. The authors acknowledge thermal projection data
sourced from HighResCoralStress datasets, larval transition probability data derived from
the eReefs GBR1 hydrodynamic model, and spatial and depth data available from the Great
Barrier Reef Marine Park Authority. The eReefs Project is a public-private collaboration
between Australia’s leading operational and scientific research agencies, government, and
corporate Australia.
